---
title: "542_project4"
author: "Tanfu Shi, Machi Takeda, Navya Gupta"
date: "2024-12-14"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
team contribution: We first worked on the assignment individually, and then worked together to compare/discuss the results, improve the code, and generate the final report. Therefore, everyone in this group contributed equally to complete this assignment.

## load package and data
```{r}
library(dplyr)
library(ggplot2)
library(recommenderlab)
library(DT)
library(data.table)
library(reshape2)

myurl = "https://liangfgithub.github.io/MovieData/"

ratings <- read.csv("C:/Users/14946/Downloads/Rmat.csv", row.names = 1)

```

##popularity
The most popular is defined by the one with highest average scores
```{r}
avg_ratings <- colMeans(ratings, na.rm = TRUE)
rating_count <- colSums(!is.na(ratings))

# 筛选流行电影
popular_movies <- data.frame(
  MovieID = colnames(ratings),
  AvgRating = avg_ratings,
  RatingCount = rating_count
) %>%
  filter(AvgRating > 4, RatingCount >= 50) %>%
  arrange(desc(AvgRating), desc(RatingCount)) %>%
  head(10)

# 输出流行电影
print(popular_movies)

```
algorithm
```{r}
cosine_similarity_sparse <- function(mat) {
  mat <- mat[, colSums(mat^2) > 0, drop = FALSE] # 移除全零列
  mat <- mat[rowSums(mat^2) > 0, , drop = FALSE] # 移除全零行
  
  sim <- as.matrix(crossprod(mat))  # 列与列的点积
  norms <- sqrt(colSums(mat^2))     # 每列的范数
  sim <- sim / outer(norms, norms)  # 归一化
  diag(sim) <- NA                   # 设置对角线为 NA
  return(round(sim, 7))             # 精确到小数点后 7 位
}


myIBCF <- function(newuser, similarity_matrix, k = 10, global_mean = NULL) {
  predictions <- numeric(ncol(similarity_matrix))
  names(predictions) <- colnames(similarity_matrix)
  
  for (i in seq_along(predictions)) {
    if (is.na(newuser[i])) { # 如果用户未评分该电影
      similar_items <- order(similarity_matrix[i, ], decreasing = TRUE, na.last = NA)[1:k]
      similarities <- similarity_matrix[i, similar_items]
      user_ratings <- newuser[similar_items]
      
      # 计算分子和分母
      numerator <- sum(similarities * user_ratings, na.rm = TRUE)
      denominator <- sum(similarities, na.rm = TRUE)
      
      # 计算预测评分
      if (denominator > 0) {
        raw_prediction <- numerator / denominator + mean(user_ratings, na.rm = TRUE)
        predictions[i] <- raw_prediction
      } else {
        # 分母为 0 时使用全局均值或流行度作为回退值
        fallback_prediction <- if (!is.null(global_mean)) global_mean else mean(newuser, na.rm = TRUE)
        predictions[i] <- fallback_prediction
      }
    }
  }
  
  # 移除 NA 值并归一化到 0-5 范围
  predictions <- na.omit(predictions)  # 移除 NA 值
  min_pred <- min(predictions, na.rm = TRUE)
  max_pred <- max(predictions, na.rm = TRUE)
  predictions <- 5 * (predictions - min_pred) / (max_pred - min_pred)  # 线性归一化
  
  # 排序并返回前 k 个结果
  return(sort(predictions, decreasing = TRUE, na.last = NA)[1:k])
}



# 加载评分矩阵
ratings_sparse <- as(as.matrix(ratings), "sparseMatrix")

# 中心化评分矩阵
row_means <- rowMeans(as.matrix(ratings_sparse), na.rm = TRUE)
row_means[is.na(row_means)] <- mean(row_means, na.rm = TRUE) # 用全局均值替换 NaN
centered_ratings <- sweep(as.matrix(ratings_sparse), 1, row_means, FUN = "-", check.margin = FALSE)
centered_ratings[is.na(centered_ratings)] <- 0 # 替换剩余的 NA 为 0
centered_ratings_sparse <- as(centered_ratings, "sparseMatrix")

# 生成相似矩阵
similarity_matrix <- cosine_similarity_sparse(centered_ratings_sparse)


```
test
```{r}
user_u1181 <- as.numeric(ratings_sparse["u1181", ])
names(user_u1181) <- colnames(ratings_sparse)
recommendations_u1181 <- myIBCF(user_u1181, similarity_matrix)
print("Top 10 recommendations for user 'u1181':")
print(data.frame(
  MovieID = names(recommendations_u1181),
  PredictedRating = recommendations_u1181
))

# 假设用户的推荐
hypothetical_user <- rep(NA, ncol(similarity_matrix))
names(hypothetical_user) <- colnames(similarity_matrix)
hypothetical_user["m1613"] <- 5
hypothetical_user["m1755"] <- 4
recommendations_hypothetical <- myIBCF(hypothetical_user, similarity_matrix)
print("Top 10 recommendations for the hypothetical user:")
print(data.frame(
  MovieID = names(recommendations_hypothetical),
  PredictedRating = recommendations_hypothetical
))

```
shiny app
```{r}
library(shiny)

# 将本地路径映射到 Shiny 的 Web 路径 "/MovieImages"
addResourcePath("MovieImages", "C:/Users/14946/Downloads/MovieImages/MovieImages/")

# 定义 UI
ui <- fluidPage(
  titlePanel("Movie Recommender System"),
  
  sidebarLayout(
    sidebarPanel(
      h4("Rate the following movies (1-5):"),
      
      # 动态生成评分输入框和照片
      uiOutput("movie_inputs"),
      
      actionButton("submit", "Get Recommendations")
    ),
    
    mainPanel(
      h4("Top 10 Movie Recommendations:"),
      tableOutput("recommendations"),  # 显示推荐结果
      uiOutput("movie_images")         # 动态展示推荐电影的图片
    )
  )
)

# 定义服务器逻辑
server <- function(input, output, session) {
  # 随机选择 5 部电影供评分
  random_movies <- reactive({
    sample(colnames(similarity_matrix), 5, replace = FALSE) # 随机选择 5 部电影
  })
  
  # 动态生成评分输入框和照片
  output$movie_inputs <- renderUI({
    movie_ids <- random_movies()
    lapply(movie_ids, function(movie) {
      numeric_id <- gsub("m", "", movie) # 如果需要去掉 "m"，只保留数字部分
      tags$div(
        style = "margin-bottom: 20px;",
        tags$img(src = paste0("/MovieImages/", numeric_id, ".jpg"), 
                 height = "150px", width = "100px", style = "display: block; margin-bottom: 5px;"),
        numericInput(
          inputId = paste0("movie_", movie),
          label = paste("Rate movie", numeric_id, "(1-5):"),
          value = NA, min = 1, max = 5
        )
      )
    })
  })
  
  # 监听用户点击 "Get Recommendations" 按钮
  observeEvent(input$submit, {
    # 初始化用户评分向量
    new_user <- rep(NA, ncol(similarity_matrix))
    names(new_user) <- colnames(similarity_matrix)
    
    # 获取用户评分
    rated_movies <- random_movies()
    for (movie in rated_movies) {
      movie_input_id <- paste0("movie_", movie)
      new_user[movie] <- input[[movie_input_id]]
    }
    
    # 生成推荐
    recommendations <- myIBCF(new_user, similarity_matrix)
    
    # 输出推荐结果到表格
    output$recommendations <- renderTable({
      data.frame(
        MovieID = names(recommendations),
        PredictedRating = recommendations
      )
    })
    
    # 动态生成推荐电影的图片展示
    output$movie_images <- renderUI({
      lapply(names(recommendations), function(movie_id) {
        numeric_id <- gsub("m", "", movie_id) # 如果需要去掉 "m"，只保留数字部分
        tags$div(
          style = "display: inline-block; margin: 10px; text-align: center;",
          tags$h5(paste("Movie:", numeric_id)),
          tags$img(src = paste0("/MovieImages/", numeric_id, ".jpg"), 
                   height = "150px", width = "100px"),
          tags$br()
        )
      })
    })
  })
}

# 启动 Shiny 应用
shinyApp(ui = ui, server = server)

```



